# Reproducible Research: Peer Assessment 1
This paper will look into a sample collected over a two-month period, October
and November 2012. The data consists of 5 minutes intervals counting the steps
the subject took.   
We will process the data, looking at what the mean and the median number of 
steps pr. day is, along with imputing missing data in order to enhance the 
precision of the dataset. Lastly, we will look at how the number of steps
differ from weekend to weekdays.

## Loading and preprocessing the data
As the data comes in a .zip format, we will unzip the data, load it, read it
and delete the unzipped folder.
For this to work the working directory must be set to the 
*RepData_PeerAssessment1* folder.

```{r, unzip}
permwd <- getwd() ## As we change the wd, we keep the original
temp <- tempfile()
unzip("activity.zip", exdir=temp)
setwd(temp) 
df <- read.csv(file="activity.csv")
unlink(temp, recursive=TRUE) ## Deletes the temp file
setwd(permwd)
```

## What is mean total number of steps taken per day?
Now that we have loaded the data, we want to look at the mean steps taken pr.
day. For this we will use the tapply function to sum the days and the baseplot
to construct a histogram.

```{r}

stepsum <- as.numeric(tapply(df$step, df$date, sum, na.rm=TRUE))
hist(stepsum, breaks=20, main = "Number of steps pr. day", xlab="Steps", ylab="Count", col="green")
meanstep <- round(mean(stepsum), 2)
medianstep <- median(stepsum)
```

We can see that the mean is `r meanstep` and the median is `r medianstep`. 


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
